Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-07-30 writeup/abbreviated/abbreviated.tex
Add Bayes nets for nms-dominated cluster 1
Add c1 summares to abbreviated
Add pamk/ASW k estimation, start writeup table

$k$-means clustering with $k = 4$ was tried. $k = 2, 3$ provided models that
were too simplistic. $k = 5$ did not provide any new information, but rather
just fragmented existing groups.

\begin{table}[h]
  \centering
  \caption{Cluster statistics}
  \label{tab:cluster_stats}
  \begin{tabular}{l|l}
    Cluster & $n$ \\
    \hline
    1 & 189 \\
    2 & 88 \\
    3 & 221 \\
    4 & 406 \\
  \end{tabular}
\end{table}

@@

\subsection{Bayesian Networks}

In Figure~\ref{fig:bnets}. Structure is too sparse, need to discretize or use
some kind of regularization (e.g. a lasso)

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{bnets.pdf}
  \caption{Bayesian Networks}
  \label{fig:bnets}
\end{figure}

>>>>

$k$-means clustering with $k = 4$ was tried. Statistics for determining the
optimal number of clusters were used, but were inconclusive: results in
Figure~\ref{tab:numclus}. This probably indicates that the data is not very
well clustered. $k = 2, 3$ provided models that were too simplistic. $k = 5$
did not provide any new information, but rather just fragmented existing
groups.

\begin{table}[h]
  \centering
  \caption{caption}
  \label{tab:numclus}
  \begin{tabular}{l|l}
    Criterion & Optimal $k$ \\
    \hline
    Minimum ASW & Inconclusive  \\
    % TODO: Finish this
  \end{tabular}
\end{table}
\begin{table}[h]
  \centering
  \caption{Cluster statistics}
  \label{tab:cluster_stats}
  \begin{tabular}{l|l}
    Cluster & $n$ \\
    \hline
    1 & 189 \\
    2 & 88 \\
    3 & 221 \\
    4 & 406 \\
  \end{tabular}
\end{table}

@@

\subsection{Bayesian Networks on Cluster 1}

Figures~\ref{fig:bnet-gs},~\ref{fig:bnet-hc}, and~\ref{fig:bnet-mmhc} show various
learning algorithms.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{clus1-bnet-gs.pdf}
  \caption{Grow Shrink Algorithm}
  \label{fig:bnet-gs}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{clus1-bnet-hc.pdf}
  \caption{Hill Climbing Algorithm}
  \label{fig:bnet-hc}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{clus1-bnet-mmhc.pdf}
  \caption{Min-Max Hill Climbing Algorithm}
  \label{fig:bnet-mmhc}
\end{figure}

\subsection{$k$-means on Cluster 1}

Figures~\ref{fig:c1-summaries-2},~\ref{fig:c1-summaries-3},
and~\ref{fig:c1-summaries-4}.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{c1-summaries-2.pdf}
  \caption{$k = 2$}
  \label{fig:c1-summaries-2}
\end{figure}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{c1-summaries-3.pdf}
  \caption{$k = 3$}
  \label{fig:c1-summaries-3}
\end{figure}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{c1-summaries-4.pdf}
  \caption{$k = 4$}
  \label{fig:c1-summaries-4}
\end{figure}
